---
title: 'PSA001: Stage 2 RR Analyses'
output:
  html_document:
    code_folding: hide
    number_sections: true
    toc: yes
    toc_depth: 5
---

# Load Data

```{r libraries, messages = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(psych) # for SPSS-style PCA
pacman::p_load(paran) # for parallel analyses
pacman::p_load(GPArotation) # for robustness checks
pacman::p_load(kableExtra) # for nice tables
pacman::p_load(tidyverse) # for data cleaning

# create directory for saving figures
if (!dir.exists("figures")) { dir.create("figures") }

options(knitr.kable.NA = '')
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE)

R.version.string

set.seed(8675309)
```

## Simulate Study Data (for Stage 1 RR)

See https://osf.io/87rbg/ for Stage 1 RR code. The code below is modified from the original to account for a different raw data structure and to add additional tables and graphs. All analysis code is identical.

## Load Study Data (for Stage 2 RR)

Load study data and demographic questionnaires from the data folder.

```{r data-load}
session <- read_csv("data/psa001_session.csv")
dat_quest <- read_csv("data/psa001_quest_data.csv")
dat_exp <- read_csv("data/psa001_exp_data.csv")

# reshape questionnaire data to make wide
quest <- dat_quest %>%
  dplyr::select(session_id, endtime, user_id, q_name, dv) %>%
  dplyr::group_by(session_id, user_id, q_name) %>%
  dplyr::arrange(endtime) %>%
  dplyr::filter(row_number() == 1) %>%
  dplyr::ungroup() %>%
  tidyr::spread(q_name, dv, convert = TRUE)
```

Join experiment and questionnaire data

```{r exp-quest-join}
ratings_raw <- dat_exp %>%
  dplyr::left_join(session, by = c("user_id", "session_id")) %>% # join session info into exp data
  dplyr::filter(user_status %in% c("guest", "registered")) %>%
  tidyr::separate(exp_name, c("psa", "language", "trait", "block"), 
           sep = "_") %>%
  dplyr::select(-psa) %>%
  tidyr::separate(proj_name, c("psa", "lang", "lab1", "lab2"),
           sep = "_", fill = "right") %>%
  dplyr::filter(lab1 != "test") %>%
  tidyr::unite(lab_id, c("lab1", "lab2")) %>%
  dplyr::select(-psa, lang) %>%
  dplyr::left_join(quest, by = c("session_id", "user_id")) %>% # join questionnaire data into the joint data
  dplyr::select(language, user_id = session_id, trait, 
                stim_id = trial_name, 
                order, rt, rating = dv,
                country, sex, age, ethnicity, 
                lab = lab_id, block) %>%
  dplyr::mutate(trait = recode(trait,
                        "Res" = "responsible",
                        "Wei" = "weird",
                        "Old" = "old",
                        "Tru" = "trustworthy",
                        "Dom" = "dominant",
                        "Emo" = "emostable",
                        "Agg" = "aggressive",
                        "Car" = "caring",
                        "Int" = "intelligent",
                        "Unh" = "unhappy",
                        "Soc" = "sociable",
                        "Mea" = "mean",
                        "Con" = "confident",
                        "Att" = "attractive"
  ))

# write_csv(ratings_raw, "data/psa001_ratings_raw.csv")

```


## Load Auxillary Data

Data on regions and stimuli.

### Load Region Data

```{r load-region}
regions <- read_csv("data/regions.csv")
```

### Load Stimulus Info

```{r load-stim-info}
stim_info <- read_csv("data/psa001_cfd_faces.csv") %>%
  mutate(ethnicity = recode(Race, "A" = "asian", "B" = "black", "L" = "latinx", "W" = "white"),
         gender = recode(Gender, "M" = "male", "F" = "female")
  )

stim_info %>%
  group_by(ethnicity, gender) %>%
  summarise(
    n = n(),
    mean_age = round(mean(Age), 2),
    sd_age = round(sd(Age), 2)
  ) %>%
  knitr::kable("html") %>%
  kable_styling("striped")

stim_n_male <- sum(stim_info$gender == "male")
stim_n_female <- sum(stim_info$gender == "female")
mean_age <- mean(stim_info$Age) %>% round(2)
sd_age <- sd(stim_info$Age) %>% round(2)
min_age <- min(stim_info$Age)
max_age <- max(stim_info$Age)
```

Stimuli in our study will be an open-access, full-color, face image set consisting of `r stim_n_male` men and `r stim_n_female` women (mean age=`r mean_age` years, SD=`r sd_age` years, range=`r min_age` to `r max_age` years), taken under standardized photographic conditions (Ma et al., 2015). 

### Load O&T 2008 Data

```{r otdata}
# read original OT data and get into same format as data_agg will be

traits <- ratings_raw %>%
  filter(trait != "old", !is.na(trait)) %>%
  arrange(trait) %>%
  pull(trait) %>%
  unique()
  
ot_data <- readxl::read_excel("data/Karolinska_14trait_judgmentswithlabels.xls") %>%
  mutate(region = "(Oosterhof & Todorov, 2008)") %>%
  rename(stim_id = `Todorov Label`,
         emostable = `emotionally stable`) %>%
  dplyr::select(region, stim_id, traits)
```


## Data Processing

### Join Data

```{r join-data}

ratings <- ratings_raw %>%
  rename(qcountry = country) %>%
  separate(lab, c("country", "lab")) %>%
  left_join(regions, by = "country") %>%
  filter(trait != "old")
  
```

### Graph distributions for trait by region
```{r plot-styles}
# plot styles
bgcolor <- "white"
textcolor <- "black"
PSA_theme <- theme(
    plot.background = element_rect(fill = bgcolor, color = NA),
    panel.background = element_rect(fill = NA, color = "grey"),
    legend.background = element_rect(fill = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    text = element_text(color = textcolor, size=15),
    axis.text = element_text(color = textcolor, size=10),
    strip.text.y = element_text(angle = 0, hjust = 0)
  )
```

```{r trait-by-region-plot, fig.width=15, fig.height=6}

ggplot(ratings, aes(rating, fill = trait)) +
  geom_histogram(binwidth = 1, color = "grey", show.legend = F) +
  facet_grid(region~trait, space = "free") +
  scale_x_continuous(breaks = 1:9) +
  PSA_theme
```

## Data checks

```{r data-checks}
part <- ratings %>%
  group_by(user_id, sex, age, country, language, trait, region, lab) %>%
  summarise(trials = n(),
            stim_n = n_distinct(stim_id)) %>%
  ungroup()
```

### How many participants completed at least one rating for each of 120 stimuli

```{r rated-1-stim}
part %>% 
  mutate(n120 = ifelse(stim_n == 120, "rated all 120", "rated < 120")) %>%
  count(region, n120) %>%
  spread(n120, n) %>%
  knitr::kable("html") %>%
  kable_styling("striped")
```

### Participants who did not complete exactly 240 trials

```{r rated-lt-240}
part %>% 
  mutate(n240 = case_when(
    trials == 240 ~ "rated 240", 
    trials > 240 ~ "rated > 240",
    trials < 120 ~ "rated < 120",
    trials < 240 ~ "rated 120-239"
  )) %>%
  count(region, n240) %>%
  spread(n240, n, fill = 0) %>%
  knitr::kable("html") %>%
  kable_styling("striped")
```

### Participants with low-variance responses in block 1

```{r low-variance}

identical_rating_threshold <- 0.75 * 120 # use this for registered analyses

inv_participants <- ratings %>%
  filter(block == 1) %>%
  count(user_id, region, trait, rating) %>%
  group_by(user_id, region, trait) %>%
  filter(n == max(n)) %>% # find most common rating for each P
  ungroup() %>%
  filter(n >= identical_rating_threshold) # select Ps who gave the same rating to >= 75% of stimuli

inv <- inv_participants %>%
  count(region, trait) %>%
  spread(region, n, fill = 0) %>%
  mutate(TOTAL = rowSums(dplyr::select_if(., is.numeric), na.rm = T))

inv_total <-  group_by(inv) %>% 
  summarise_if(is.numeric, sum, na.rm = T) %>%
  mutate(trait = "TOTAL")
 
bind_rows(inv,inv_total) %>%
  knitr::kable("html") %>%
  kable_styling("striped")
```


### Participants with no region

```{r no-region}
part %>% 
  filter(is.na(region)) %>%
  dplyr::select(user_id, country, lab)
```


### Remove excluded data and average ratings

```{r data-exclusions}
data <- ratings %>%
  group_by(user_id, trait) %>%
  filter(
    # did not complete 1+ ratings for each of 120 stimuli
    dplyr::n_distinct(stim_id) == 120,      
    !is.na(region)   # did not specify region (none expected)
  ) %>%
  anti_join(inv_participants, by = "user_id") %>% # exclude Ps with low variance
  ungroup() %>%
  group_by(user_id, age, sex, ethnicity, language, lab, country, region, trait, stim_id) %>%
  summarise(rating = mean(rating)) %>% # average ratings across 2 
  ungroup()

write_csv(data, "data/psa001_ind.csv")

```



## Participant Demographics

```{r demog-language}
data %>%
  group_by(user_id, language) %>%
  summarise() %>%
  ungroup() %>%
  group_by(language) %>%
  summarise(n = n()) %>%
  knitr::kable("html") %>%
  kable_styling("striped")
```

```{r demog-region}
by_region <- data %>%
  group_by(user_id, region) %>%
  summarise() %>%
  ungroup() %>%
  group_by(region) %>%
  summarise(n = n()) %>%
  add_row(region = "TOTAL", n = n_distinct(data$user_id)) %>%
  knitr::kable("html") %>%
  kable_styling("striped")

save_kable(by_region, "figures/n_by_region.html")
           
by_region
```

### Age and sex distribution per region
```{r age-sex-plot, fig.width=12, fig.height=10}
data %>%
  group_by(user_id, sex, age, region) %>%
  summarise() %>%
  ungroup() %>%
  group_by(region) %>%
  mutate(n = n()) %>%
  ungroup() %>%
  ggplot(aes(as.numeric(age), fill = sex)) +
  geom_histogram(binwidth = 5, color = "grey") +
  geom_text(aes(x=0, y=5, label = paste0("n=",n)), color = "black") +
  labs(title="", y="", x="Participant age in 5-year bins") +
  facet_grid(region~., scales="free_y") +
  PSA_theme
```


### Participants per trait per region

```{r n-trait-region-plot, fig.width=15, fig.height=10.5}
data %>%
  group_by(trait, region) %>%
  summarise(n = n_distinct(user_id)) %>%
  ggplot(aes(trait, n)) +
  geom_col(aes(fill = trait), show.legend = F) +
  geom_hline(yintercept = 15) +
  facet_grid(region~., scale = "free") +
  labs(title="", x="", y="Participants per trait per region") +
  theme( axis.text.x = element_text(angle = -45, hjust = 0) ) + 
  PSA_theme

ggsave("figures/participants_per_trait_per_region.png", width = 15, height = 8)
```

### Participants per lab

```{r n-per-lab}
labs <- data %>%
  unite(lab, country, lab) %>%
  group_by(region, lab, user_id) %>%
  summarise() %>%
  ungroup() %>%
  count(region, lab) %>%
  arrange(region, lab)

knitr::kable(labs) %>%
  kable_styling("striped")
```


# Analyses

## Main Analysis

First, we will calculate the average rating for each face separately for each of the 13 traits. Like Oosterhof and Todorov (2008), we will then subject these mean ratings to principal component analysis with orthogonal components and no rotation. Using the criteria reported in Oosterhof and Todorov’s (2008) paper, we will retain and interpret the components with an Eigenvalue > 1. 

### Calculate Alphas

```{r calc-alphas, eval = FALSE}

# takes a long time, so saves the results and loads from a file in the next chunk if set to eval = FALSE
data_alpha <- data %>%
  dplyr::select(user_id, region, stim_id, rating, trait) %>%
  spread(stim_id, rating, sep = "_") %>%
  group_by(trait, region) %>%
  nest() %>%
  mutate(alpha = map(data, function(d) {
    if (dim(d)[1] > 2) {
      # calculate cronbach's alpha
      subdata <- d %>%
        as_tibble() %>%
        dplyr::select(-user_id) %>%
        t()

      capture.output(suppressWarnings(a <- psych::alpha(subdata)))
      a$total["std.alpha"] %>% pluck(1) %>% round(3)
    } else {
      NA
    }
  })) %>%
  dplyr::select(-data) %>%
  unnest(alpha) %>%
  ungroup()

saveRDS(data_alpha, file = "data/alphas.RDS")
```

```{r alpha-table}

data_alpha <- readRDS("data/alphas.RDS")

n_alpha <- data %>%
  dplyr::select(user_id, region, trait) %>%
  distinct() %>%
  count(region, trait) %>%
  left_join(data_alpha, by = c("region", "trait")) %>%
  mutate(
    trait = as.factor(trait),
    region = str_replace(region, " (and|&) ", " &\n"),
    region = as.factor(region),
    region = factor(region, levels = rev(levels(region)))
  )

n_alpha %>%
  mutate(stat = paste("α =", alpha, "<br>n =", n)) %>%
  dplyr::select(Region = region, stat, trait) %>%
  spread(trait, stat) %>%
  knitr::kable("html", escape = FALSE) %>%
  column_spec(2:14, width = "7%") %>%
  kable_styling("striped", font_size = 9) %>%
  save_kable("figures/alpha.html")
```

```{r alpha-plot, fig.width=18, fig.height=10}

ggplot(n_alpha) +
  geom_tile(aes(trait, region, fill=alpha >=.7), 
           color = "grey20", show.legend = F) +
  geom_text(aes(trait, region, label=sprintf("α = %0.2f\nn = %.0f", alpha, n)), color = "black", size = 5) +
  scale_y_discrete(drop=FALSE) +
  scale_x_discrete(position = "top") +
  labs(x="", y="", title="") +
  scale_fill_manual(values = c("white", "red")) +
  PSA_theme

ggsave("figures/alphas.png", width = 18, height = 10)

```


### Calculate Aggregate Scores

```{r calc-agg-scores}

data_agg <- data %>%
  group_by(region, trait, stim_id) %>%
  summarise(rating = mean(rating)) %>%
  ungroup() %>%
  spread(trait, rating)

write_csv(data_agg, "data/psa001_agg.csv")

```

```{r agg-plot, fig.width=15, fig.height = 8}
data_agg %>%
  gather("trait", "rating", aggressive:weird) %>%
  ggplot(aes(rating, fill = trait)) +
  geom_density(show.legend = F) +
  facet_grid(region~trait) +
  PSA_theme

ggsave("figures/agg_scores.png", width = 15, height = 8)
```

### Principal Component Analysis (PCA)

The number of components to extract was determined using eigenvalues > 1 for each world region. PCA was conducted using the `psych::principal()` function with `rotate="none"`.

```{r pca-function}
# function to calculate PCA

psa_pca <- function(d) {
  traits <- dplyr::select(d, -stim_id) %>% 
    dplyr::select_if(colSums(!is.na(.)) > 0) # omits missing traits
  
  # principal components analysis (SPSS-style, following Oosterhof & Todorov)
  ev <- eigen(cor(traits))$values
  nfactors <- sum(ev > 1)
  
  pca <- principal(
    traits, 
    nfactors=nfactors, 
    rotate="none"
  )
  
  stats <- pca$Vaccounted %>% 
    as.data.frame() %>%
    rownames_to_column() %>%
    mutate(type = "stat")
  
  unclass(pca$loadings) %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    mutate(type = "trait") %>%
    bind_rows(stats) %>%
    gather("pc", "loading", 2:(ncol(.)-1))
}
```

```{r pca}

pca_analyses <- data_agg %>%
  bind_rows(ot_data) %>%
  group_by(region) %>%
  nest() %>%
  mutate(pca = map(data, psa_pca)) %>%
  dplyr::select(-data) %>%
  unnest(pca) %>%
  ungroup() %>%
  mutate(pc = str_replace(pc, "PC", "Component "))

```

#### Number of Components (and proportion variance) by region
```{r pca-components}
pca_analyses %>%
  filter(rowname == "Proportion Var") %>%
  group_by(region) %>%
  mutate(nPCs = n()) %>%
  ungroup() %>%
  spread(pc, loading) %>%
  dplyr::select(-rowname, -type) %>%
  mutate_if(is.numeric, round, 3) %>%
  knitr::kable("html") %>%
  kable_styling("striped")
```

#### Trait Loadings by Region and Component

```{r pca-trait-loadings, fig.width=15, fig.height=10}

# order traits by P1 loading if loads positively on P1, or by -P2 loading otherwise
trait_order <- pca_analyses %>%
  filter(region == "(Oosterhof & Todorov, 2008)", type == "trait") %>%
  spread(pc, loading) %>% 
  arrange(ifelse(`Component 1`>0,`Component 1`,-`Component 2`)) %>% 
  pull(rowname)

pca_prop_var <- pca_analyses %>%
  filter(rowname == "Proportion Var") %>%
  dplyr::select(-rowname, -type) %>%
  mutate(loading = round(loading, 2))

pca_analyses %>%
  filter(type == "trait") %>%
  dplyr::select(-type) %>%
  mutate(
    trait = as.factor(rowname),
    trait = factor(trait, levels = c(trait_order, "Prop.Var")),
    loading = round(loading, 2)
  ) %>%
  ggplot() +
  geom_tile(aes(pc, trait, fill=loading), show.legend = F) +
  geom_text(aes(pc, trait, label=sprintf("%0.2f", loading)), color = "black") +
  geom_text(data = pca_prop_var, aes(pc, y = 14, label=sprintf("%0.2f", loading)), color = "black") +
  scale_y_discrete(drop=FALSE) +
  scale_x_discrete(position = "top") + 
  scale_fill_gradient2(low = "dodgerblue", mid = "grey90", high = "#FF3333", limits=c(-1.1, 1.1)) +
  facet_wrap(~region, scales = "fixed", ncol = 4) +
  labs(x = "", y = "", title="") +
  PSA_theme

ggsave("figures/PCA_loadings.png", width = 15, height = 10)
```


#### Replication Criteria (PCA)

Oosterhof and Todorov’s valence-dominance model will be judged to have been replicated in a given world region if the first two components both have Eigenvalues > 1, the first component (i.e., the one explaining more of the variance in ratings) is correlated strongly (loading > .7) with trustworthiness and weakly (loading < .5) with dominance, and the second component (i.e., the one explaining less of the variance in ratings) is correlated strongly (loading > .7) with dominance and weakly (loading < .5) with trustworthiness. All three criteria need to be met to conclude that the model was replicated in a given world region.

```{r pca-replication-criteria}

pca_rep <- pca_analyses %>%
  filter(
    type == "trait", 
    rowname %in% c("trustworthy", "dominant"),
    pc %in% c("Component 1", "Component 2")
  ) %>%
  dplyr::select(-type) %>%
  mutate(rowname = paste(pc, rowname)) %>%
  dplyr::select(-pc) %>%
  spread(rowname, loading) %>%
  rename(Region = region) %>%
  mutate(Replicated = ifelse(
    `Component 1 dominant` < .5 & `Component 1 trustworthy` > .7 & 
    `Component 2 dominant` > .7 & `Component 2 trustworthy` < .5,
    "Yes", "No"
  )) %>%
  mutate_if(is.numeric, round, 3) %>%
  knitr::kable("html", col.names = c("Region", "Dominant", "Trustworthy", "Dominant", "Trustworthy", "Replicated")) %>%
  add_header_above(c(" " = 1, "Component 1" = 2, "Component 2" = 2, "  " = 1)) %>%
  kable_styling("striped")

save_kable(pca_rep, "figures/PCA_rep_criteria.html")

pca_rep
```

### Factor Congruence (PCA)

This analysis determines the congruence between the components from Oosterhof & Todorov (2008) and the components in each world region, using the `psych::factor.congruence` function. Congruence is labeled "not similar" for values < 0.85, "fairly similar", for values < 0.09, and "equal" for values >= 0.95.

```{r pca-factor-congruence}

# get loadings for original O&T2008
ot2008_pca_loadings <- pca_analyses %>%
  filter(region == "(Oosterhof & Todorov, 2008)", type == "trait") %>%
  dplyr::select(-region, -type) %>%
  spread(pc, loading) %>%
  column_to_rownames()

# run factor congruence for each region  
fc_pca <- pca_analyses %>%
  filter(type == "trait", region != "(Oosterhof & Todorov, 2008)") %>%
  dplyr::select(-type) %>%
  spread(pc, loading) %>%
  group_by(region) %>%
  nest() %>%
  mutate(fc = map(data, function(d) {
    loadings <- d %>%
      as.data.frame() %>%
      dplyr::select(rowname, `Component 1`, `Component 2`) %>%
      arrange(rowname) %>%
      column_to_rownames()
    
    psych::factor.congruence(loadings, 
                             ot2008_pca_loadings, 
                             digits = 4) %>%
      as.data.frame() %>%
      rownames_to_column(var = "regionPC")
  })) %>%
  dplyr::select(-data) %>%
  unnest(fc) %>%
  ungroup()

pc_fc_table <- fc_pca %>%
  gather(origPC, congruence, `Component 1`:`Component 2`) %>%
  mutate(sig = case_when(
           congruence < .85 ~ "not similar",
           congruence < .95 ~ "fairly similar",
           congruence >= .95 ~ "equal"
         ),
         congruence = sprintf("%0.3f", congruence)) %>%
  filter(regionPC == origPC) %>%
  dplyr::select(region, PC = regionPC, congruence, sig) %>%
  gather(k, v, congruence, sig) %>%
  unite(PC, PC, k, remove = T) %>%
  spread(PC, v) %>%
  knitr::kable("html", digits = 3, align = 'lrlrl', escape = F,
               col.names = c("Region", "Loading", "Congruence", "Loading", "Congruence")) %>%
  add_header_above(c(" " = 1, "Component 1" = 2, "Component 2" = 2)) %>%
  kable_styling("striped")

save_kable(pc_fc_table, "figures/PCA_factor_congruence.html")

pc_fc_table
```

## Robustness Checks

### Exploratory Factor Analysis (EFA)

The number of factors to extract was determined using parallel analysis (`paran::paran()`) for each world region. EFA was conducted using the `psych::fa()` function with all default options.

```{r efa-function}
# function to calculate EFA

psa_efa <- function(d) {
  traits <- dplyr::select(d, -stim_id) %>% 
    dplyr::select_if(colSums(!is.na(.)) > 0) # omits missing traits
  
  # Parallel Analysis with Dino's 'paran' package. 
  nfactors <- paran(traits, iterations = 5000, 
          centile = 0, quietly = TRUE, 
          status = FALSE, all = TRUE, 
          cfa = TRUE, graph = FALSE)
  
  efa <- psych::fa(traits, nfactors$Retained) 
  
  stats <- efa$Vaccounted %>% 
    as.data.frame() %>%
    rownames_to_column() %>%
    mutate(type = "stat")
  
  unclass(efa$loadings) %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    mutate(type = "trait") %>%
    bind_rows(stats) %>%
    gather("mr", "loading", 2:(ncol(.)-1))
}
```

Calculate for each region

```{r efa, message=FALSE, results="hide"}

efa_analyses <- data_agg %>%
  bind_rows(ot_data) %>%
  group_by(region) %>%
  nest() %>%
  mutate(efa = map(data, psa_efa)) %>%
  dplyr::select(-data) %>%
  unnest(efa) %>%
  ungroup() %>%
  mutate(mr = str_replace(mr, "MR", "Factor "))

```

#### Number of Factors (and proportion variance) by region

Note: the analysis for USA & Canada produced a warning: "The estimated weights for the factor scores are probably incorrect.  Try a different factor extraction method."

```{r efa-factors}
efa_analyses %>%
  filter(rowname == "Proportion Var") %>%
  group_by(region) %>%
  mutate(nMRs = n()) %>%
  ungroup() %>%
  spread(mr, loading) %>%
  dplyr::select(-rowname, -type) %>%
  mutate_if(is.numeric, round, 3) %>%
  knitr::kable("html") %>%
  kable_styling("striped")
```

#### Trait Loadings by Region and Factor

```{r efa-trait-loadings, fig.width=15, fig.height=10}

efa_prop_var <- efa_analyses %>%
  filter(rowname == "Proportion Var") %>%
  dplyr::select(-rowname, -type) %>%
  mutate(loading = round(loading, 2))

efa_analyses %>%
  filter(type == "trait") %>%
  dplyr::select(-type) %>%
  mutate(
    trait = as.factor(rowname),
    trait = factor(trait, levels = c(trait_order, "Prop.Var")),
    loading = round(loading, 2)
  ) %>%
  ggplot() +
  geom_tile(aes(mr, trait, fill=loading), show.legend = F) +
  geom_text(aes(mr, trait, label=sprintf("%0.2f", loading)), color = "black") +
  geom_text(data = efa_prop_var, aes(mr, y = 14, label=sprintf("%0.2f", loading)), color = "black") +
  scale_y_discrete(drop=FALSE) +
  scale_x_discrete(position = "top") + 
  scale_fill_gradient2(low = "dodgerblue", mid = "grey90", high = "#FF3333", limits=c(-1.1, 1.1)) +
  facet_wrap(~region, scales = "fixed", ncol = 4) +
  labs(x = "", y = "", title="") +
  PSA_theme

ggsave("figures/EFA_loadings.png", width = 15, height = 10)
```


#### Replication Criteria (EFA)

Oosterhof and Todorov’s valence-dominance model will be judged to have been replicated in a given world region if the the first factor is correlated strongly (loading > .7) with trustworthiness and weakly (loading < .5) with dominance, and the second factor is correlated strongly (loading > .7) with dominance and weakly (loading < .5) with trustworthiness. All these criteria need to be met to conclude that the model was replicated in a given world region.

```{r efa-replication-criteria}

efa_rep <- efa_analyses %>%
  filter(
    type == "trait", 
    rowname %in% c("trustworthy", "dominant"),
    mr %in% c("Factor 1", "Factor 2")
  ) %>%
  dplyr::select(-type) %>%
  mutate(rowname = paste(mr, rowname)) %>%
  dplyr::select(-mr) %>%
  spread(rowname, loading) %>%
  rename(Region = region) %>%
  mutate(Replicated = ifelse(
    `Factor 1 dominant` < .5 & `Factor 1 trustworthy` > .7 & 
    `Factor 2 dominant` > .7 & `Factor 2 trustworthy` < .5,
    "Yes", "No"
  )) %>%
  mutate_if(is.numeric, round, 3) %>%
  knitr::kable("html", col.names = c("Region", "Dominant", "Trustworthy", "Dominant", "Trustworthy", "Replicated")) %>%
  add_header_above(c(" " = 1, "Factor 1" = 2, "Factor 2" = 2, "  " = 1)) %>%
  kable_styling("striped")

save_kable(efa_rep, "figures/EFA_rep_criteria.html")

efa_rep

```

### Factor Congruence (EFA)

This analysis determines the congruence between the factors from Oosterhof & Todorov (2008) and the factors in each world region, using the `psych::factor.congruence` function. Congruence is labeled "not similar" for values < 0.85, "fairly similar", for values < 0.09, and "equal" for values >= 0.95.

```{r efa-factor-congruence}

# get loadings for original O&T2008
ot2008_efa_loadings <- efa_analyses %>%
  filter(region == "(Oosterhof & Todorov, 2008)", type == "trait") %>%
  dplyr::select(-region, -type) %>%
  spread(mr, loading) %>%
  column_to_rownames()

# run factor congruence for each region 
fc_efa <- efa_analyses %>%
  filter(type == "trait", region != "(Oosterhof & Todorov, 2008)") %>%
  dplyr::select(-type) %>%
  spread(mr, loading) %>%
  group_by(region) %>%
  nest() %>%
  mutate(fc = map(data, function(d) {
    loadings <- d %>%
      as.data.frame() %>%
      dplyr::select(rowname, `Factor 1`, `Factor 2`) %>%
      arrange(rowname) %>%
      column_to_rownames()
    
    psych::factor.congruence(loadings, 
                             ot2008_efa_loadings, 
                             digits = 4) %>%
  as.data.frame() %>%
  rownames_to_column(var = "regionMR")
  })) %>%
  dplyr::select(-data) %>%
  unnest(fc) %>%
  ungroup()

mr_fc_table <- fc_efa %>%
  gather(origMR, congruence, `Factor 1`:`Factor 2`) %>%
  mutate(sig = case_when(
           congruence < .85 ~ "not similar",
           congruence < .95 ~ "fairly similar",
           congruence >= .95 ~ "equal"
         ),
         congruence = sprintf("%0.3f", congruence)) %>%
  filter(regionMR == origMR) %>%
  dplyr::select(region, MR = regionMR, congruence, sig) %>%
  gather(k, v, congruence, sig) %>%
  unite(MR, MR, k, remove = T) %>%
  spread(MR, v) %>%
  knitr::kable("html", digits = 3, align = 'lrlrl', 
               col.names = c("Region", "Loading", "Congruence", "Loading", "Congruence")) %>%
  add_header_above(c(" " = 1, "Factor 1" = 2, "Factor 2" = 2)) %>%
  kable_styling("striped")


save_kable(mr_fc_table, "figures/EFA_factor_congruence.html")

mr_fc_table
```

